Sparse Function-space Representation \\ of Neural Networks

### 2023-05-15 paper/main.tex
re added greedy objective

We consider environments with states \(\state \in \stateDomain \subseteq \R^{D_{\state}} \),
actions \(\action \in \actionDomain \subseteq \R^{D_{\action}}\) and transition dynamics
\(\transitionFn: \stateDomain \times \actionDomain \rightarrow \stateDomain \), such that
$\state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t}$, where  $\noise_{t}$
is i.i.d. transition noise.
We consider the episodic setting where the system is reset to an initial state $\state_{0}$ at each episode and we
assume that there is a known reward function $r : \stateDomain \times \actionDomain \rightarrow \R$.
% Following the Markov decision process formulation \cite{bellmanMarkovianDecisionProcess1957a}, we
% denote the states \(\state \in \stateDomain \subseteq \R^{D_{\state}} \) and actions \(\action \in \actionDomain \subseteq \R^{D_{\action}}\)
% of the sytem, the reward function $r : \stateDomain \times \actionDomain \rightarrow \R$, and transition dynamics
% \(\transitionFn: \stateDomain \times \actionDomain \rightarrow \stateDomain \), such that
% $\state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t}$ where  $\noise_{t}$
% is i.i.d. transition noise.
% $\mathbb{E}_{\noise_{0:\infty}} \big[ \sum_{t=0}^{\infty} \discount^{t} \rewardFn(\state_{t},\action_{t}) \big]$
% \begin{align} \label{eq-model-free-objective}
% \policy^{*} = \arg \max_{\policy \in \policyDomain} J(\transitionFn, \policy) = \arg \max_{\policy \in \policyDomain} \mathbb{E}_{\noise_{0:\infty}} \bigg[ \sum_{t=0}^{\infty} \discount^{t} \rewardFn(\state_{t},\action_{t}) \bigg]
% \quad \text{s.t. } \state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t},
% \end{align}
The goal of RL is to find the policy \(\pi : \stateDomain \rightarrow \actionDomain\)
(from a set of policies $\Pi$) that maximises the sum of discounted rewards
in expectation over the transition noise,
\begin{align} \label{eq-model-free-objective}
J(\transitionFn, \policy) = \mathbb{E}_{\noise_{0:\infty}} \bigg[ \sum_{t=0}^{\infty} \discount^{t} \rewardFn(\state_{t},\action_{t}) \bigg]
\quad \text{s.t. } \state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t},
\end{align}
where $\gamma \in [0, 1)$ is a discount factor.
In this work, we consider model-based RL where a model of the transition dynamics is learned \(f_{\mathbf{w}} \approx \transitionFn\) and then used by a planning algorithm.
A simple approach is to use the learned dynamic model $f_{\mathbf{w}^{*}}$ and maximise the objective in \cref{eq-model-free-objective}.
% \begin{align} \label{eq-greedy}
%   \policy^{\text{Greedy}} &= \arg \max_{\pi \in \Pi} J(f_{\mathbf{w}^{*}}, \pi).
% \end{align}
However, we can leverage the method in \cref{sec:methods} to obtain a function-space posterior over the learned dynamics $q_{\mathbf{u}}(\hat{\transitionFn} \mid \dataset)$,
where $\mathcal{D}$ represents the state transition data set \(\mathcal{D} = \{(s_{i},a_{i}), s_{i+1}\}_{i=0}^{N}\).
Importantly, the uncertainty represented by this posterior distribution can be used to balance the exploration-exploitation trade-off,
using approaches such as posterior sampling \cite{osbandWhyPosteriorSampling2017,osbandMoreEfficientReinforcement2013},
\begin{align} \label{eq-posterior-sampling}
  \policy^{\text{PS}} &= \arg \max_{\pi \in \Pi} J(\hat{f}, \pi)
\quad \text{s.t. } \tilde{\transitionFn} \sim q_{\mathbf{u}}(\hat{\transitionFn} \mid \dataset),
\end{align}
where a function $\tilde{\transitionFn}$ is sampled from the (approximate) posterior $q_{\mathbf{u}}(\hat{\transitionFn} \mid \dataset)$ and used to find a policy as
in \cref{eq-greedy}.
Intuitively, this strategy will explore where the model has high uncertainty, which in turn will reduce the model's uncertainty as data is collected and used to
train the model.
See \cref{sec-rl-appendix} for more details of how we use

>>>>

We consider environments with states \(\state \in \stateDomain \subseteq \R^{D_{\state}} \),
actions \(\action \in \actionDomain \subseteq \R^{D_{\action}}\) and transition dynamics
\(\transitionFn: \stateDomain \times \actionDomain \rightarrow \stateDomain \), such that
$\state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t}$, where  $\noise_{t}$
is i.i.d. transition noise.
We consider the episodic setting where the system is reset to an initial state $\state_{0}$ at each episode and we
assume that there is a known reward function $r : \stateDomain \times \actionDomain \rightarrow \R$.
% Following the Markov decision process formulation \cite{bellmanMarkovianDecisionProcess1957a}, we
% denote the states \(\state \in \stateDomain \subseteq \R^{D_{\state}} \) and actions \(\action \in \actionDomain \subseteq \R^{D_{\action}}\)
% of the sytem, the reward function $r : \stateDomain \times \actionDomain \rightarrow \R$, and transition dynamics
% \(\transitionFn: \stateDomain \times \actionDomain \rightarrow \stateDomain \), such that
% $\state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t}$ where  $\noise_{t}$
% is i.i.d. transition noise.
% $\mathbb{E}_{\noise_{0:\infty}} \big[ \sum_{t=0}^{\infty} \discount^{t} \rewardFn(\state_{t},\action_{t}) \big]$
% \begin{align} \label{eq-model-free-objective}
% \policy^{*} = \arg \max_{\policy \in \policyDomain} J(\transitionFn, \policy) = \arg \max_{\policy \in \policyDomain} \mathbb{E}_{\noise_{0:\infty}} \bigg[ \sum_{t=0}^{\infty} \discount^{t} \rewardFn(\state_{t},\action_{t}) \bigg]
% \quad \text{s.t. } \state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t},
% \end{align}
The goal of RL is to find the policy \(\pi : \stateDomain \rightarrow \actionDomain\)
(from a set of policies $\Pi$) that maximises the sum of discounted rewards
in expectation over the transition noise,
\begin{align} \label{eq-model-free-objective}
J(\transitionFn, \policy) = \mathbb{E}_{\noise_{0:\infty}} \bigg[ \sum_{t=0}^{\infty} \discount^{t} \rewardFn(\state_{t},\action_{t}) \bigg]
\quad \text{s.t. } \state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t},
\end{align}
where $\gamma \in [0, 1)$ is a discount factor.
In this work, we consider model-based RL where a model of the transition dynamics is learned \(f_{\mathbf{w}} \approx \transitionFn\) and then used by a planning algorithm.
A simple approach is to use the learned dynamic model $f_{\mathbf{w}^{*}}$ and maximise the objective in \cref{eq-model-free-objective},
\begin{align} \label{eq-greedy}
  \policy^{\text{Greedy}} &= \arg \max_{\pi \in \Pi} J(f_{\mathbf{w}^{*}}, \pi).
\end{align}
However, we can leverage the method in \cref{sec:methods} to obtain a function-space posterior over the learned dynamics $q_{\mathbf{u}}(\hat{\transitionFn} \mid \dataset)$,
where $\mathcal{D}$ represents the state transition data set \(\mathcal{D} = \{(s_{i},a_{i}), s_{i+1}\}_{i=0}^{N}\).
Importantly, the uncertainty represented by this posterior distribution can be used to balance the exploration-exploitation trade-off,
using approaches such as posterior sampling \cite{osbandWhyPosteriorSampling2017,osbandMoreEfficientReinforcement2013},
\begin{align} \label{eq-posterior-sampling}
  \policy^{\text{PS}} &= \arg \max_{\pi \in \Pi} J(\hat{f}, \pi)
\quad \text{s.t. } \tilde{\transitionFn} \sim q_{\mathbf{u}}(\hat{\transitionFn} \mid \dataset),
\end{align}
where a function $\tilde{\transitionFn}$ is sampled from the (approximate) posterior $q_{\mathbf{u}}(\hat{\transitionFn} \mid \dataset)$ and used to find a policy as
in \cref{eq-greedy}.
Intuitively, this strategy will explore where the model has high uncertainty, which in turn will reduce the model's uncertainty as data is collected and used to
train the model.
See \cref{sec-rl-appendix} for more details of how we use
